### 2019-07-02 README.rmd

<!--
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/ggalluvial)](https://cran.r-project.org/package=ggalluvial)
-->

>>>>

[![Travis build status](https://travis-ci.org/corybrunson/ggalluvial.svg?branch=master)](https://travis-ci.org/corybrunson/ggalluvial)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/ggalluvial)](https://cran.r-project.org/package=ggalluvial)
